Homeostatic mechanisms may shape the type and duration of oscillatory modulation.

### 2019-04-22 main.tex
Updates from Overleaf
Added missing source code url

We prepose the same mechanisms that link homeostasis with chemical neuromodulation can also come into play during oscillatory modulation. After all, both kinds of modulation lead to tonic changes in spiking and in Ca\textsuperscript{2+} concentration, which can in turn drives changes to intrinsic homeostasis \cite{Liu1998}.

@@

After homeostatic equilibrium is reached, we measure two features: the synchrony between action potentials (measured by the Kappa correlation) and changes in the excitability of the system (measured as a change in population firing rate). Both of which are defined in the \textit{Methods}. To ensure a consistent comparison between experiments, measurements were made over the same 4-cycle or 0.5 second period in all simulations.

>>>>

We propose the same mechanisms that link homeostasis with chemical neuromodulation can also come into play during oscillatory modulation. After all, both kinds of modulation lead to tonic changes in spiking and in Ca\textsuperscript{2+} concentration, which can in turn drives changes to intrinsic homeostasis \cite{Liu1998}.

@@

After homeostatic equilibrium is reached, we measure two features: the synchrony between action potentials (measured by the Kappa correlation) and changes in the excitability of the system (measured as a change in population firing rate). Both of which are defined in the \textit{Methods}. To ensure a consistent comparison between experiments, measurements were made over the same 4-cycle or 0.5 second period in all simulations. Source code for all simulations is available at \url{https://github.com/voytekresearch/resistingrhythm}
